---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# pifpaf

<!-- badges: start -->
<!-- badges: end -->

The goal of pifpaf is to estimate potential impact fractions and population attributable fractions using individual-level or aggregate data. 

## Installation

You can install the most updated version of pifpaf as follows:

``` r
library(devtools)
devtools::install_github("colleenchan/pifpaf")
```

## Example

This is a basic example which shows you how to estimate the PAF when 
individual-level exposure data is available to the user, where the relative
risk function takes the form $\text{RR}(\beta x) = \exp(\beta x) = 1.27$ with variance 
0.002.

```{r}
library(pifpaf)
# generate some exposure data
set.seed(1)
x <- rweibull(1000, 1.2, 1.66) 

# Estimate PAF
pif.ind(x, beta = log(1.27), varbeta = 0.002)
```


For the PIF, we allow counterfactual exposures of the form $g(x) = a + bx$. 
```{r}
# Estimate PIF for a counterfactual exposure of a 1 unit decrease
pif.ind(x, beta = log(1.27), varbeta = 0.002, a = -1)

# Estimate PIF for a counterfactual exposure of 50% decrease
pif.ind(x, beta = log(1.27), varbeta = 0.002, b = 0.5)
```




Now suppose the user does not have access to the individual-level exposure data
but does know its mean and variance. This is typical in publications, where 
only the mean and variance are reported. We can approximate the PAF using only
the first two moments. In this example, the mean of the exposure is 1.55 with 
variance 1.6.

``` r
paf.app(meanx = 1.55, varx = 1.6, n = 1000, beta = log(1.27), varbeta = 0.002)

```

